---
title: "Timeseries Honeywell"
author: "Akshay"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##We first load the libraries and the data file

```{r}
library(forecast)
library(ggplot2)

ts_honey <-  read.csv("Honeywell.csv")
ts_honey <- ts_honey[c(-1,-3)]

ts_honey <- ts(ts_honey)
plot.ts(ts_honey)

```

#Perform analysis on time seris data using Exponential smoothing and varying alpha to see which has the least SSE

```{r}
mod1 <- HoltWinters(ts_honey, alpha=0.15, beta=FALSE, gamma=FALSE)
mod2 <- HoltWinters(ts_honey, alpha=0.35, beta=FALSE, gamma=FALSE)

mod3 <- HoltWinters(ts_honey, alpha=0.55, beta=FALSE, gamma=FALSE)
mod4 <- HoltWinters(ts_honey, alpha=0.75, beta=FALSE, gamma=FALSE)
modauto <- HoltWinters(ts_honey,  beta=FALSE, gamma=FALSE)


mod1$SSE
mod2$SSE
mod3$SSE
mod4$SSE
modauto$SSE

modforecast <- forecast(modauto, h = 4)
modforecast
plot(modforecast)

```

##Changing the beta parameter on HoltzWinters
```{r}
ts_honey <-  read.csv("Honeywell.csv")

ts_honey <- ts_honey[c(-1,-3)]


mod1 <- HoltWinters(ts_honey, alpha=0.75, beta=0.15, gamma=FALSE)
mod2 <- HoltWinters(ts_honey, alpha=0.75, beta=0.25, gamma=FALSE)

mod3 <- HoltWinters(ts_honey, alpha=0.75, beta=0.45, gamma=FALSE)
mod4 <- HoltWinters(ts_honey, alpha=0.75, beta=0.85, gamma=FALSE)
modauto <- HoltWinters(ts_honey,   gamma=FALSE)


mod1$SSE
mod2$SSE
mod3$SSE
mod4$SSE
modauto$SSE

modforecast <- forecast(modauto, h = 4)

plot(modforecast)
```

Performing the prediction using linear regression and comparing it with time series forecast.
```{r}
ts_honey <-  read.csv("Honeywell.csv")
ts_honey <- ts_honey[c(-1,-3)]
num <- seq(1:124)
ts_honey[,2] <- num
temp <- ts_honey[,1] 
ts_honey[,1] <- ts_honey[,2]
ts_honey[,2] <- temp


df <- lm(ts_honey$V2 ~ ts_honey$Close)

plot(df)

ggplot(ts_honey,aes(x=V2,y=Close)) + geom_point(aes(color = Close)) + scale_colour_gradient(high='red',low = "blue") + geom_smooth(method='lm',formula=y~x)


summary(df)
new <- data.frame(x = seq(124, 247, 1))

prediction <- predict(df, newdata = new,se.fit = TRUE)

mean((ts_honey[,2] - prediction$fit)^2)

sse <- sum(df$residuals^2)

sse

summary(df)

X <- resid(df)

hist(X)
View(X)

#Plotting probability plot
qqnorm(X) 
qqline(X)

ts_honey <-  read.csv("Honeywell.csv")

plot(ts_honey$Date,X, type = "p")

plot(X,prediction$fit, type = "p")
abline(df)
```

##We can see from the above plot how badly the linear refression has performed for prediction compared to forecast using Exponential smoothing.